%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{hyperref}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{color}
\renewcommand\labelitemi{\normalfont\bfseries --}

\setlength{\textwidth}{6.1in} % Text width of the document


\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Fabien Baradel} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
\moveleft.5\hoffset\centerline{Ph.D. Candidate, INSA-Lyon} % Your address
\moveleft.5\hoffset\centerline{Email: \href{fabien.baradel@gmail.com}{fabien.baradel@gmail.com}}
\moveleft.5\hoffset\centerline{Web: \href{fabienbaradel.github.io}{fabienbaradel.github.io}}
\setlength\parindent{0em}
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{\large Research Interests}  
Deep/Machine Learning, Computer Vision, Video Understanding, Visual Reasoning, Causal Inference

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\large Education}
\textbf{INSA-Lyon} \hfill Lyon, France \hfill October 2016 - Present \\
Ph.D., Computer Science
\begin{itemize}
\item  Thesis: {\sl "Structured Deep Learning for Video Analysis"}
\item  Supervisors: Christian Wolf - Julien Mille
\item  Expected defense: June 2020
\end{itemize}


\textbf{ENSAI} \hfill Rennes, France \hfill September 2013 - June 2016 \\
M.Sc, Statistics \& Computer Science
\begin{itemize}
\item Suma Cum Laude (top of class) - High Honors
\item "Diplôme d'ingénieur" from the National School of Statistics and Data Analysis
\end{itemize}

\textbf{University of Warwick} \hfill Coventry, UK \hfill January 2015 - June 2015 \\
M.Sc, Statistics
\begin{itemize}
\item Erasmus Mundus semester exchange (First-class honors)
\end{itemize}

\textbf{University of Paris Dauphine} \hfill Paris, France \hfill January 2015 - June 2015 \\
B.Sc, Applied Economics
\begin{itemize}
\item Double agreement with ENSAI
\end{itemize}

\textbf{University of Grenoble Alps} \hfill Grenoble, France \hfill September 2010 - June 2013 \\
B.Sc, Applied Mathematics
\begin{itemize}
\item Suma Cum Laude (top of class) - High Honors
\end{itemize}
 
%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{\large Work Experience} 

<<<<<<< HEAD
\textbf{Google} \hfill Grenoble, France \hfill April 2019 - Mars 2020 \\
Student Researcher Intern --- Perception team
=======
\textbf{Google} \hfill Grenoble, France \hfill April 2019 - Present \\
Student Researcher intern --- Ganesha team
>>>>>>> 1354e2537e583208460bfde50cd475228f1cb2ac
\begin{itemize}
\item \textit{"Self-supervised learning from video data"} advised by Cordelia Schmid and Chen Sun
\item Learning without annotation from visual and audio signals from large-scale video datasets
\end{itemize}

\textbf{Simon Fraser Univeristy} \hfill Vancouver, Canada \hfill February 2018 - June 2018 \\
Visiting researcher --- Vision \& Media Lab
\begin{itemize}
\item \textit{"Human-Object interaction in Videos"} advised by Greg Mori
\end{itemize}

\textbf{University of Guelph} \hfill Guelph, Canada \hfill Summer 2017 \\
Visiting researcher --- Machine Learning Research Group
\begin{itemize}
\item \textit{"Trimmed Video Classification"} advised by Graham Taylor
\end{itemize}

\textbf{INSA-Lyon - LIRIS} \hfill Lyon, France \hfill October 2016 - Present \\
Doctoral Researcher --- Imagine team
\begin{itemize}
\item \textit{"Deep Learning for Human Understanding"} advised by Christian Wolf and Julien Mille
\item Research on computer vision and machine learning with a focus on human activity recognition and video understanding. Animation of weekly group lecture meeting. Collaboration with N. Neverova (Research Scientist at Facebook Research AI).
\end{itemize}

\textbf{XRCE} \hfill Grenoble, France \hfill March 2016 - September 2016 \\
Research Intern --- Machine Learning for Services
\begin{itemize}
\item Xerox Research Centre Europe (now NAVER Labs Europe)
\item \textit{"Unsupervised domain adaptation for image recognition"} advised by  Boris Chidlovskii and Gabriela Csurka
\end{itemize}

\textbf{LICIT - IFSTTAR} \hfill Lyon, France \hfill June 2015 - August 2015 \\
Research Intern
\begin{itemize}
\item \textit{"Machine Learning for road traffic forecasting"} advised by Romain Billot
\end{itemize}

%----------------------------------------------------------------------------------------

\section{\large Conference Publications} 
\begin{enumerate}[wide=0pt]
	\item \textbf{F. Baradel}, N. Neverova, J. Mille, G. Mori, C. Wolf. "CoPhy: Counterfactual Learning of Physical Dynamics", \textit{The International Conference on Learning Representations (\textbf{ICLR})}. 2020. \textbf{Spotlight}.
	\item \textbf{F. Baradel}, N. Neverova, C. Wolf, J. Mille, G. Mori. "Object Level Visual Reasoning in Videos", \textit{The IEEE European Conference on Computer Vision (\textbf{ECCV})}. 2018.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille. "Human Activity Recognition with Pose-driven Attention to RGB", \textit{The British Machine Vision Conference (\textbf{BMVC})}. 2018.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille, G. W. Taylor. "Glimpse Clouds: Human Activity Recognition from Unstructured Feature Points", \textit{The IEEE Computer Vision and Patter Recognition (\textbf{CVPR})}. 2018.
\end{enumerate}


%----------------------------------------------------------------------------------------

\section{\large Workshop Publications}
\begin{enumerate}[wide=0pt]
<<<<<<< HEAD
	\item C. Sun, \textbf{F. Baradel}, K. Murphy, C. Schmid. "Contrastive Bidirectional Transformer for Temporal Representation Learning", \textit{The IEEE European Conference in Computer Vision (ECCV)}. 2020.
	\item \textbf{F. Baradel}, N. Neverova, J. Mille, G. Mori, C. Wolf. "CoPhy: Counterfactual Learning of Physical Dynamics", \textit{The International Conference in Representation Learning (ICLR)}. 2020. Spotlight presentation.% \textbf{3 citations}.
	\item \textbf{F. Baradel}, N. Neverova, C. Wolf, J. Mille, G. Mori. "Object Level Visual Reasoning in Videos", \textit{The IEEE European Conference on Computer Vision (ECCV)}. 2018.% \textbf{3 citations}.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille. "Human Activity Recognition with Pose-driven Attention to RGB", \textit{The British Machine Vision Conference (BMVC)}. 2018.% \textbf{1 citation}.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille, G. W. Taylor. "Glimpse Clouds: Human Activity Recognition from Unstructured Feature Points", \textit{The IEEE Computer Vision and Patter Recognition (CVPR)}. 2018.% \textbf{13 citations}.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille. "Human Action Recognition: Pose-based Attention draws focus to Hands", \textit{The IEEE International Conference on Computer Vision (ICCV), Workshop "Hands in Action"}. 2017.% \textbf{16 citations}.
	\item G. Csurka, \textbf{F. Baradel}, B. Chidlovskii, S. Clinchant. "Discrepancy-based networks for unsupervised domain adaptation: a comparative study",  \textit{The IEEE International Conference on Computer Vision (ICCV), Workshop "Task-CV"}. 2017.% \textbf{4 citations}.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille. "Pose-conditioned Spatio-Temporal Attention for Human Action Recognition",  \textit{arXiv pre-print arXiv:1703.10106}. 2017.% \textbf{18 citations}.
=======
	\item \textbf{F. Baradel}, C. Wolf, J. Mille. "Human Action Recognition: Pose-based Attention draws focus to Hands", \textit{The IEEE International Conference on Computer Vision (\textbf{ICCV}), Workshop "Hands in Action"}. 2017.
	\item G. Csurka, \textbf{F. Baradel}, B. Chidlovskii, S. Clinchant. "Discrepancy-based networks for unsupervised domain adaptation: a comparative study",  \textit{The IEEE International Conference on Computer Vision (\textbf{ICCV}), Workshop "Task-CV"}. 2017.
>>>>>>> 1354e2537e583208460bfde50cd475228f1cb2ac
\end{enumerate}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\section{\large ArXiv Preprints} 
\begin{enumerate}[wide=0pt]
	\item C. Sun, \textbf{F. Baradel}, K. Murphy, C. Schmid. "Learning Video Representations using Contrastive Bidirectional Transformer", \textit{arXiv:1906.05743}. 2019.
	\item \textbf{F. Baradel}, C. Wolf, J. Mille. "Pose-conditioned Spatio-Temporal Attention for Human Action Recognition",  \textit{arXiv:1703.10106}. 2017.
\end{enumerate}

%----------------------------------------------------------------------------------------

\section{\large Patents}
\begin{enumerate}[wide=0pt]
	\item \textbf{F. Baradel}, B. Chidlovskii, G. Csurka. "Conditional adaptation network for image classification",  \textit{US Patent - 15450620}. 2017.
\end{enumerate}

<<<<<<< HEAD
\section{\large Reviewer}  
ECCV 2020, ICCV 2019, ICML 2019, CVPR 2019-2020, FG 2019, NIPS 2018, IJCV, TNNLS
=======
%----------------------------------------------------------------------------------------

\section{\large Talks}
"Visual Reasoning in Videos",  \textit{GDR ISIS-IA "Reasoning from Visual Signal"}. October 2018. \\
"Pose and Attention for Action Recognition", \textit{GDR ISIS "Pose and Gesture"}. December 2017.

%----------------------------------------------------------------------------------------

\section{\large Press Coverage}
\href{https://www.rsipvision.com/CVPR2018-Tuesday/14/}{\textbf{CVPR Daily 2018}}: "Glimpse Clouds for Human Activity Understanding".
>>>>>>> 1354e2537e583208460bfde50cd475228f1cb2ac

\section{\large Teaching Experience}
\textbf{Sciences-U} \hfill Lyon, France \hfill 2018-2019 \\
Lecturer
\begin{itemize}
	\item \textit{Introduction to Machine Learning} - (M2) - (CM+TD+TP - 30h)
\end{itemize}

\textbf{Univ. Lyon 1} \hfill Lyon, France \hfill Fall 2017 \\
Teaching Assistant
\begin{itemize}
	\item \textit{Regression modelling}  - (M2 Data Science) - (TP - 12h)
	\item \textit{Probability \& Statistics}  - (L2 Info \& MathsEco) - (TP - 20h)
\end{itemize}

\textbf{EPITA} \hfill Lyon, France \hfill September 2017 \\
Teaching Assistant
\begin{itemize}
	\item \textit{Mathematics} - (L1) - (CM+TD - 24h)
\end{itemize}

\textbf{ENSAI} \hfill Rennes, France \hfill January 2017 \\
Seminar
\begin{itemize}
\item \textit{Introduction to Deep Learning with Tensorflow} - (MSc Data Science) - (6h)
\end{itemize}

%----------------------------------------------------------------------------------------

\section{\large Awards and Honors} 
ANR/NSERC Ph.D. Fellowship - DeepVision project \\
Erasmus Mundus exchange program scholarship

%----------------------------------------------------------------------------------------

\section{\large Professional Services}
\textbf{Conference reviewer}: ECCV 2020, CVPR 2019-2020, ICML 2019, NIPS 2018 \\
\textbf{Journal reviewer}: IJCV, TNNLS

%----------------------------------------------------------------------------------------

\section{\large Computer Skills} 
Python, Java, SQL, PHP, R, SAS \\
PyTorch, Tensorflow, FFMPEG, \LaTeX, Linux, Mac, HTML, CSS

%----------------------------------------------------------------------------------------

\end{resume}
\end{document}
